---
title: "hw6_jw4007"
output: github_document
---


```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(p8105.datasets)

set.seed(1)
```
## Q2
### Importing data
```{r}
homicide_url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicide = read.csv(homicide_url) %>% janitor::clean_names()

homicide %>% group_by(victim_age) %>% summarize()
```

### Create a city_state variable and a binary variable indicating whether the homicide is solved. Omit cities, limit "victim_race" is white or black. Mutate "victim_age" as a numeric variable.
```{r}
homicide_analyze = homicide %>% 
  mutate(case_solve = if_else(disposition == "Closed by arrest", 1, 0),
         city_state = str_c(city, state, sep = ","),
         victim_age = as.numeric(victim_age)) %>%
  filter(city_state != "Dallas,TX",
         city_state != "Phoenix,AZ", 
         city_state != "Kansas City,MO", 
         city_state != "Tulsa,AL") %>% 
  filter(victim_race == "White" | victim_race == "Black")
  
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.
```{r}
Baltimore_glm = lm(case_solve ~ victim_age + victim_sex + victim_race, data = homicide_analyze) %>% 
  broom::tidy() 

Baltimore_glm %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(lower_bound = exp(estimate - 1.96*std.error),
         upper_bound = exp(estimate + 1.96*std.error),
         odds_ratio = exp(estimate)) %>% 
  select(estimate, odds_ratio, lower_bound, upper_bound) %>% knitr::kable(digits = 2)
```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.
```{r}
homicide_male_vs_female = homicide_analyze %>% 
  nest(data = !city_state) %>% 
  mutate(models = map(.x = data, ~lm(case_solve ~ victim_age + victim_sex + victim_race, data = .x)),
         results = map(models, broom::tidy)) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(lower_bound = exp(estimate - 1.96*std.error),
         upper_bound = exp(estimate + 1.96*std.error),
         OR_male_vs_female = exp(estimate)) %>% 
  select(city_state, estimate, OR_male_vs_female, lower_bound, upper_bound) 

knitr::kable(homicide_male_vs_female, digits = 2)
  
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}
homicide_male_vs_female %>% 
  mutate(city_state = fct_reorder(city_state, OR_male_vs_female, .desc = TRUE)) %>% 
  ggplot(aes(x = OR_male_vs_female, y = city_state)) + 
  geom_point() +
  geom_errorbar(aes(xmin = lower_bound, xmax = upper_bound))
```

## Q3

```{r}
birthweight = read.csv("./birthweight.csv") %>% 
  janitor::clean_names() 

birthweight %>% 
  summarize(n = sum(is.na(birthweight)))
```


```{r}
birthweight = birthweight %>% 
  mutate(babysex = as.factor(babysex),
         delwt_kg = delwt * 0.4536,
         malform = as.factor(malform),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         mheight_cm = mheight * 2.54,
         ppwt_kg = ppwt * 0.4536,
         wtgain_kg = wtgain * 0.4536) 
```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
birthweight_hyp = lm(bwt ~ blength + babysex + malform, data = birthweight) 

birthweight %>% 
  add_predictions(birthweight_hyp) %>% 
  add_residuals(birthweight_hyp) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point() 
```

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.
```{r}
birthweight_cv = 
  crossv_mc(birthweight, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(hyp = map(train, ~lm(bwt ~ blength + babysex + malform, data = .x)),
         main = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         interaction = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(rmse_hyp = map2_dbl(hyp, test, ~rmse(model = .x, data = .y)),
         rmse_main = map2_dbl(main, test, ~rmse(model = .x, data = .y)),
         rmse_interaction = map2_dbl(interaction, test, ~rmse(model = .x, data = .y)))


```


```{r}
birthweight_cv %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(everything(),
               names_to = "model",
               values_to = "rmse",
               names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_boxplot()

```

